Speed and strength of epidemic intervention

### 2019-07-09 doc/speedstrength.tex
stuff
update
tweak

\begin{itemize}
	\item $L(\tau)$ represents intervention over the course of infection
	\item Then, $\hat K(\tau) = K(\tau)/L(\tau)$
	\item Define intervention strength:
	$$
	\theta = 1/\langle 1/L(\tau) \rangle_{g(\tau)},
	$$
	harmonic mean of $L(\tau)$ weighted by generation-interval distribution; outbreak controlled if $\theta > \mathcal R$ (not affected by $\RR$)
	\item Define intervention speed ($\phi = r - \hat r$):
	$$
	1 = \langle \frac{\exp(\phi \tau) }{L(\tau)} \rangle_{b(\tau)}
	$$
	sort of a mean associated with $L(\tau)$; outbreak controlled if $\phi > r$ (not affected by $r$).
\end{itemize}

\subsection{HIV example}

\begin{itemize}
	\item Can active testing and treatment stop the epidemic?
	\item Explain different scenarios? assumptions?
	\item Early vs late transmission (change proportion of early transmission)
	\item Compare required strength and speed of intervention required to control the disease
\end{itemize}

\section{Results}

\begin{itemize}
	\item Early transmission matters for condom
	\item Early transmission doesn't matter so much for target and treat
	\item Think about speed vs strength axis
\end{itemize}

>>>>

\begin{itemize}
	\item $L(\tau)$ represents intervention over the course of infection
	\item Then, $\hat K(\tau) = K(\tau)/L(\tau)$
	\item Define intervention strength:
	$$
	\theta = 1/\langle 1/L(\tau) \rangle_{g(\tau)},
	$$
	harmonic mean of $L(\tau)$ weighted by generation-interval distribution; outbreak controlled if $\theta > \mathcal R$ (not affected by $\RR$)
	\item Define intervention speed ($\phi = r - \hat r$):
	$$
	1 = \left\langle \frac{\exp(\phi \tau) }{L(\tau)} \right\rangle_{b(\tau)}
	$$
	sort of a mean associated with $L(\tau)$; outbreak controlled if $\phi > r$ (not affected by $r$).
\end{itemize}

\section{Examples}

\subsection{Test and treatment - HIV}

\begin{itemize}
	\item Can active testing and treatment stop the epidemic?
	\item Explain different scenarios? assumptions?
	\item Early vs late transmission (change proportion of early transmission)
	\item Compare required strength and speed of intervention required to control the disease
	\item Early transmission matters for condom
	\item Early transmission doesn't matter so much for target and treat
	\item Think about speed vs strength axis
\end{itemize}

\subsection{Asymptomatic infection}

\begin{itemize}
	\item See ``Factors that make an infectious disease outbreak controllable'' by Fraser et al.
	\item Our framework generalizes their work
	\item Timing of target intervention (Fraser works on this stuff and did a clinical trial on this; unpublished)
\end{itemize}

\subsection{Maybe one more example}
